Child Signals of Need in Utila, Honduras: An Exploratory Study

### 2024-09-25 Paper.qmd
Analysis script: Added corrplots. Fixed plots for the main models with signaling as the outcome. Added code exploring alloparenting.
Paper:
Added code to source dictionary. Minor dictionary changes.

```{r setup, include=FALSE}
source("analysisforpaper.R", local = knitr::knit_global())

@@

|                                 |                                                                                                                   |
|--------------------------|----------------------------------------------|
| Variable                        | Survey question wording                                                                                           |
| Crying Frequency                | How often does your child cry?                                                                                    |
| Sad Frequency                   | How often is your child sad?                                                                                      |
| Tantrum Frequency               | How often does your child throw temper tantrums? (e.g., scream, throws things, or throws themselves on the floor) |
| Running Away Frequency          | How often does your child leave the house without telling you when they get mad?                                  |
| Parent/Child Conflict Frequency | How often do you have conflicts with your child?                                                                  |
| Child Alloparenting Frequency   | How often does your child take care of their other siblings?                                                      |

@@

: The conversions from Likert scale to count value for the frequencies of child behaviors included in this study. Variables created with this scheme include the frequencies of sadness, crying, temper tantrums, conflict with primary caretakers, and child alloparenting effort.

@@

|                     |                                                                                                  |
|--------------------------|----------------------------------------------|
| Variable            | Survey question wording                                                                          |
| Relative Need       | How much time, effort, and resources does this child need compared to your other children?       |
| Relative Investment | How much time, effort, and resources do you put into this child compared to your other children? |

@@

|                        |                                                                                       |
|--------------------------|----------------------------------------------|
| Variable               | Survey question wording                                                               |
| IllnessSusceptibility1 | If an illness is 'going around', my child will get it.                                |
| IllnessSusceptibility2 | In general, my child is very susceptible to colds, flu, and other infectious diseases |
| IllnessSusceptibility3 | My child’s immune system protects him/her from most illnesses that other kids get.    |

@@

```{r sumtab_children}
#| label: tbl-sumtab_children
#| tbl-cap: Summary statistics for child study variables.
vars_c <- c(
  ChildAge = "Age (years)",
  SadFreqN = "Sad frequency (times per month)",
  CryFreqN = "Crying frequency (times per month)",
  TantrumFreqN = "Temper tantrum frequency (times per month)",
  AlloparentingFreqN = "Frequency of child's own alloparetning effort (times per month)",
  ConflictFreqN = "Frequency of conflict with focal caretaker (times per month)",
  SignalFreq = "Frequency of signals summed (times per month)",
  SignalCost = "Signal cost",
  SignalFreqMax = "Frequency of most common signal (times per month)",
  IllnessSusceptibility1 = "IllnessSusceptibility1",
  IllnessSusceptibility2 = "IllnessSusceptibility2",
  IllnessSusceptibility3 = "IllnessSusceptibility3",
  IllnessSusceptibilityMean = "Mean of current health measures",
  HeightZ = "Height Z-score (CDC)",
  WeightZ = "Weight Z-score (CDC)",
  BMIZ = "BMI Z-score (CDC)",
  SubscapMean = "Subscapular skinfold thickness (mm)",
  SubscapR = "Subscapular skinfold residuals",
  TricepMean = "Tricep skinfold thickness (mm)",
  TricepR = "Tricep skinfold residuals",
  BodyFat =  "Body fat composite"
)

@@

```{r}
#| label: tbl-conflict_dep_var
#| tbl-cap: Regression table for the model examining the frequency of conflict between child and caretaker as the dependent variable.
r_vars <- c(
  ChildAge = "Age (years)",
  SexMale = "Sex (male)",
  OtherChildrenHH = "Other children",
  LogIncome = "Income (log)",
  number_adults = "Adults in home",
  PartnerStatusUnpartnered = "Partner status (single)",
  EducationLevelYears = "Parent ed. (years)",
  ConflictFreqN = "Conflict freq.",
  SignalFreq = "Signal freq.",
  SignalCost = "Signal cost",
  SignalFreqMax = "Max signal freq.",
  IllnessSusceptibilityMean = "Percieved illness susceptibility",
  SadFreqN = "Sadness freq.",
  CryFreqN = "Crying freq.",
  TantrumFreqN = "Tantrum freq.",
  AlloparentingFreqN = "Child allocare",
  TricepR = "Tricep skinfold (residuals)",
  SubscapR = "Subscapular skinfold (residuals)",
  BodyFat = "BodyFat (composite)",
  RelativeNeed3 = "Relative need (w/in household)",
  UnwantedTask = "Unwanted task",
  Punishment21 = "Punishment",
  Family21 = "Family conflict",
  DiscomfortPainInjuryIllness = "Discomfort/Pain/Injury/Illness",
  CaregiverResponse = "Caregiver Response",
  OlderKids = "Older children",
  YoungerKids = "Younger children",
  AdultsNoChildcare = "Adults that do not provide childcare",
  AdultsChildcare = "Adults that provide childcare",
  OtherChildAlloparentingFreqN = "Other household child alloparetning freq."
)
modelsummary(mconflict, gof_map = "nobs", coef_rename = r_vars, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```

@@

```{r}
#| label: tbl-alloparenting_dep_var
#| tbl-cap: Regression table for the model examining the frequency of conflict between child and caretaker as the dependent variable.
r_vars <- c(
  ChildAge = "Age (years)",
  SexMale = "Sex (male)",
  OtherChildrenHH = "Other children",
  LogIncome = "Income (log)",
  number_adults = "Adults in home",
  PartnerStatusUnpartnered = "Partner status (single)",
  EducationLevelYears = "Parent ed. (years)",
  ConflictFreqN = "Conflict freq.",
  SignalFreq = "Signal freq.",
  SignalCost = "Signal cost",
  SignalFreqMax = "Max signal freq.",
  IllnessSusceptibilityMean = "Percieved illness susceptibility",
  SadFreqN = "Sadness freq.",
  CryFreqN = "Crying freq.",
  TantrumFreqN = "Tantrum freq.",
  AlloparentingFreqN = "Child allocare",
  TricepR = "Tricep skinfold (residuals)",
  SubscapR = "Subscapular skinfold (residuals)",
  BodyFat = "BodyFat (composite)",
  RelativeNeed3 = "Relative need (w/in household)",
  UnwantedTask = "Unwanted task",
  Punishment21 = "Punishment",
  Family21 = "Family conflict",
  DiscomfortPainInjuryIllness = "Discomfort/Pain/Injury/Illness",
  CaregiverResponse = "Caregiver Response",
  OlderKids = "Older children",
  YoungerKids = "Younger children",
  AdultsNoChildcare = "Adults that do not provide childcare",
  AdultsChildcare = "Adults that provide childcare",
  OtherChildAlloparentingFreqN = "Other household child alloparetning freq."
)
modelsummary(malloparenting, gof_map = "nobs", coef_rename = r_vars, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```

>>>>

```{r setup, include=FALSE}
source("dictionaries.R")
source("analysisforpaper.R", local = knitr::knit_global()) # experiment with taking this away

@@

|                                 |                                                                                                                   |
|--------------------------|---------------------------------------------|
| Variable                        | Survey question wording                                                                                           |
| Crying Frequency                | How often does your child cry?                                                                                    |
| Sad Frequency                   | How often is your child sad?                                                                                      |
| Tantrum Frequency               | How often does your child throw temper tantrums? (e.g., scream, throws things, or throws themselves on the floor) |
| Running Away Frequency          | How often does your child leave the house without telling you when they get mad?                                  |
| Parent/Child Conflict Frequency | How often do you have conflicts with your child?                                                                  |
| Child Alloparenting Frequency   | How often does your child take care of their other siblings?                                                      |

@@

: The conversions from Likert scale to count value for the frequencies of child behaviors included in this study. Variables created with this scheme include the frequencies of sadness, crying, temper tantrums, conflict with primary caretakers, and child alloparenting effort. {#tbl-convertedfreqs}

@@

|                     |                                                                                                  |
|--------------------------|---------------------------------------------|
| Variable            | Survey question wording                                                                          |
| Relative Need       | How much time, effort, and resources does this child need compared to your other children?       |
| Relative Investment | How much time, effort, and resources do you put into this child compared to your other children? |

@@

|                        |                                                                                       |
|--------------------------|---------------------------------------------|
| Variable               | Survey question wording                                                               |
| IllnessSusceptibility1 | If an illness is 'going around', my child will get it.                                |
| IllnessSusceptibility2 | In general, my child is very susceptible to colds, flu, and other infectious diseases |
| IllnessSusceptibility3 | My child’s immune system protects him/her from most illnesses that other kids get.    |

@@

```{r sumtab_children}
#| label: tbl-sumtab_children
#| tbl-cap: Summary statistics for child study variables.
vars_c <- c(
  ChildAge = "Age (years)",
  SadFreqN = "Sad frequency (times per month)",
  CryFreqN = "Crying frequency (times per month)",
  TantrumFreqN = "Temper tantrum frequency (times per month)",
  AlloparentingFreqN = "Frequency of child's own alloparenting effort (times per month)",
  ConflictFreqN = "Frequency of conflict with focal caretaker (times per month)",
  SignalFreq = "Frequency of signals summed (times per month)",
  SignalCost = "Signal cost",
  SignalFreqMax = "Frequency of most common signal (times per month)",
  # IllnessSusceptibility1 = "IllnessSusceptibility1",
  # IllnessSusceptibility2 = "IllnessSusceptibility2",
  # IllnessSusceptibility3 = "IllnessSusceptibility3",
  IllnessSusceptibilityMean = "Illness avoidance index",
  HeightZ = "Height Z-score (CDC)",
  WeightZ = "Weight Z-score (CDC)",
  BMIZ = "BMI Z-score (CDC)",
  SubscapMean = "Subscapular skinfold thickness (mm)",
  SubscapR = "Subscapular skinfold residuals",
  TricepMean = "Tricep skinfold thickness (mm)",
  TricepR = "Tricep skinfold residuals",
  BodyFat =  "Body fat composite"
)

@@

```{r}
#| label: tbl-conflict_dep_var
#| tbl-cap: Regression table for the model examining the frequency of conflict between child and caretaker as the dependent variable.
r_vars <- c(
  ChildAge = "Age (years)",
  SexMale = "Sex (male)",
  OtherChildrenHH = "Other children",
  LogIncome = "Income (log)",
  number_adults = "Adults in home",
  PartnerStatusUnpartnered = "Partner status (single)",
  EducationLevelYears = "Parent ed. (years)",
  ConflictFreqN = "Conflict freq.",
  SignalFreq = "Signal freq.",
  SignalCost = "Signal cost",
  SignalFreqMax = "Max signal freq.",
  IllnessSusceptibilityMean = "Percieved illness susceptibility",
  SadFreqN = "Sadness freq.",
  CryFreqN = "Crying freq.",
  TantrumFreqN = "Tantrum freq.",
  AlloparentingFreqN = "Child allocare",
  TricepR = "Tricep skinfold (residuals)",
  SubscapR = "Subscapular skinfold (residuals)",
  BodyFat = "BodyFat (composite)",
  RelativeNeed3 = "Relative need (w/in household)",
  UnwantedTask = "Unwanted task",
  Punishment21 = "Punishment",
  Family21 = "Family conflict",
  DiscomfortPainInjuryIllness = "Discomfort/Pain/Injury/Illness",
  CaregiverResponse = "Caregiver Response",
  OlderKids = "Older children",
  YoungerKids = "Younger children",
  AdultsNoChildcare = "Adults that do not provide childcare",
  AdultsChildcare = "Adults that provide childcare",
  OtherChildAlloparentingFreqN = "Other household child alloparenting freq."
)
modelsummary(mconflict, gof_map = "nobs", coef_rename = r_vars, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```

@@

```{r}
#| label: tbl-alloparenting_dep_var
#| tbl-cap: Regression table for the model examining the frequency of conflict between child and caretaker as the dependent variable.
r_vars <- c(
  ChildAge = "Age (years)",
  SexMale = "Sex (male)",
  OtherChildrenHH = "Other children",
  LogIncome = "Income (log)",
  number_adults = "Adults in home",
  PartnerStatusUnpartnered = "Partner status (single)",
  EducationLevelYears = "Parent ed. (years)",
  ConflictFreqN = "Conflict freq.",
  SignalFreq = "Signal freq.",
  SignalCost = "Signal cost",
  SignalFreqMax = "Max signal freq.",
  IllnessSusceptibilityMean = "Percieved illness susceptibility",
  SadFreqN = "Sadness freq.",
  CryFreqN = "Crying freq.",
  TantrumFreqN = "Tantrum freq.",
  AlloparentingFreqN = "Child allocare",
  TricepR = "Tricep skinfold (residuals)",
  SubscapR = "Subscapular skinfold (residuals)",
  BodyFat = "BodyFat (composite)",
  RelativeNeed3 = "Relative need (w/in household)",
  UnwantedTask = "Unwanted task",
  Punishment21 = "Punishment",
  Family21 = "Family conflict",
  DiscomfortPainInjuryIllness = "Discomfort/Pain/Injury/Illness",
  CaregiverResponse = "Caregiver Response",
  OlderKids = "Older children",
  YoungerKids = "Younger children",
  AdultsNoChildcare = "Adults that do not provide childcare",
  AdultsChildcare = "Adults that provide childcare",
  OtherChildAlloparentingFreqN = "Other household child alloparenting freq."
)
modelsummary(malloparenting, gof_map = "nobs", coef_rename = r_vars, stars = c('*' = .05, '**' = .01, '***' = .001), coef_omit = "(Intercept)")
```
